% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Bandersnatch VRF-AD Specification},
  pdfauthor={Davide Galassi; Seyed Hosseini},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Bandersnatch VRF-AD Specification}
\author{Davide Galassi \and Seyed Hosseini}
\date{27 Apr 2026 - Draft 34}

\begin{document}
\maketitle

\newcommand{\G}{\bold{G}}
\newcommand{\F}{\bold{F}}
\newcommand{\S}{\bold{\Sigma}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{\texorpdfstring{\emph{Abstract}}{Abstract}}\label{abstract}

This specification defines three Verifiable Random Function with
Additional Data (VRF-AD) schemes -- Tiny VRF, Thin VRF, and Pedersen VRF
-- built on a transcript-based Fiat-Shamir transform with support for
multiple input/output pairs via delinearization. Tiny VRF and Thin VRF
are loosely inspired by IETF ECVRF
\href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381} {[}1{]},
adapted with a transcript-based Fiat-Shamir transform, support for
additional data, and multiple I/O pairs via delinearization. Pedersen
VRF follows the construction introduced by
\href{https://eprint.iacr.org/2023/002}{BCHSV23} {[}2{]} and serves as a
building block for anonymized ring signatures based on the ring proof
scheme derived from \href{https://eprint.iacr.org/2022/1205}{CSSV22}
{[}3{]}. All schemes are instantiated over the Bandersnatch elliptic
curve, constructed over the BLS12-381 scalar field as specified in
\href{https://eprint.iacr.org/2021/1152}{MSZ21} {[}4{]}.

\section{1. Preliminaries}\label{preliminaries}

\subsection{1.1. Groups and Fields}\label{groups-and-fields}

\begin{itemize}
\tightlist
\item
  \(\bold{G}\): Bandersnatch curve cyclic group of prime order \(r\),
  defined over the base field of prime order \(q\).
\item
  \(\bold{F}\): Scalar field of prime order \(r\)
  (i.e.~\(\mathbb{Z}_r\)).
\item
  \(\bold{\Sigma}^k\): Octet strings with length \(k \in \mathbb{N}\)
  (\(*\) for arbitrary length).
\item
  \(\mathcal{O}\): Identity point of \(\bold{G}\).
\end{itemize}

The EC group \(\bold{G}\) is the prime subgroup of the Bandersnatch
elliptic curve, in Twisted Edwards form, with finite field and curve
parameters as specified in
\href{https://eprint.iacr.org/2021/1152}{MSZ21} {[}4{]}. For this group,
\texttt{fLen} = \texttt{qLen} = \(32\) and \texttt{cofactor} = \(4\).

All point arithmetic MUST be performed in \(\bold{G}\). Points not in
\(\bold{G}\) MUST be rejected at all entry points; accepting a point on
the full curve but outside the prime-order subgroup enables
small-subgroup attacks that break the VRF relation.

\subsection{1.2. Notation}\label{notation}

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret key scalar.
\item
  \(Y \in \bold{G}\): Public key point defined as \(x \cdot G\).
\item
  \(i \in \bold{\Sigma}^*\): VRF input data.
\item
  \(I \in \bold{G}\): VRF input point.
\item
  \(O \in \bold{G}\): VRF output point.
\item
  \(o \in \bold{\Sigma}^k\): VRF output hash.
\item
  \(T\): Transcript state.
\end{itemize}

The \emph{group generator} \(G \in \bold{G}\) is defined as:
\[\footnotesize\begin{aligned}
x &= 18886178867200960497001835917649091219057080094937609519140440539760939937304 \\
y &= 19188667384257783945677642223292697773471335439753913231509108946878080696678
\end{aligned}\]

\subsection{1.3. VRF-AD}\label{vrf-ad}

Regardless of the specific scheme, a \emph{Verifiable Random Function
with Additional Data (VRF-AD)} can be concisely represented by three
primary functions:

\textbf{Abstract interface}:

\begin{itemize}
\tightlist
\item
  \(\texttt{prove}(x \in \bold{F}, \overline{io} \in (\bold{G}\times \bold{G})^n, ad \in \bold{\Sigma}^*) \to \Pi\)
\item
  \(\texttt{verify}(Y \in \bold{G}, \overline{io} \in (\bold{G}\times \bold{G})^n, ad \in \bold{\Sigma}^*, \Pi) \to (\top \mid \bot)\)
\item
  \(\texttt{output}(O \in \bold{G}) \to o \in \bold{\Sigma}^N\)
\end{itemize}

For Pedersen VRF (section 4), the public key \(Y\) is not an explicit
input to \(\texttt{verify}\); the proof \(\Pi\) carries a blinded
commitment \(\bar{Y}\) instead.

The additional data \(ad\) is an arbitrary-length octet-string signed
together with the VRF output. It does not influence the produced VRF
output. The length of \(ad\) MUST NOT exceed \(2^{64} - 1\) bytes, as
the length is encoded via \(\texttt{enc\_64}\) in the VRF transcript
(section 1.6.5).

\subsection{1.4. Constants}\label{constants}

\begin{itemize}
\item
  \texttt{suite\_id} = \texttt{"Bandersnatch-SHA512-ELL2-v1"} --- the
  27-byte ASCII string identifying the cipher suite. It bundles several
  tightly-coupled choices: curve (Bandersnatch in Twisted Edwards form),
  transcript construction (HashTranscript over SHA-512), nonce algorithm
  (RFC-8032 inspired), challenge derivation (transcript squeeze), point
  encoding (compressed little-endian), hash-to-curve (Elligator 2 random
  oracle), and security level (128-bit). Bump the trailing version
  suffix when any of these changes.
\item
  \texttt{challenge\_len} = 16 bytes (128-bit security).
\item
  \texttt{expanded\_scalar\_len} =
  \(\lceil(\lceil\log_2(r)\rceil + 128) / 8\rceil\) = 48 bytes.
\end{itemize}

Domain separation tags used throughout the protocol:

\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Tag & Value & Usage \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
TinyVrf & 0x00 & Tiny VRF scheme identifier \\
ThinVrf & 0x01 & Thin VRF scheme identifier \\
PedersenVrf & 0x02 & Pedersen VRF scheme identifier \\
NonceExpand & 0x10 & Nonce secret expansion \\
Nonce & 0x11 & Nonce derivation \\
PedersenBlinding & 0x12 & Pedersen blinding factor \\
PointToHash & 0x20 & VRF output hashing \\
Delinearize & 0x30 & Delinearization scalars \\
Challenge & 0x40 & Challenge derivation \\
BatchVerify & 0x50 & Batch verification randomization \\
HashToCurve & 0x60 & Hash-to-curve domain separation \\
\end{longtable}

\subsection{1.5. Codec}\label{codec}

\begin{itemize}
\tightlist
\item
  \(\texttt{enc\_scalar}(s \in \bold{F})\): Encodes a scalar into 32
  octets in little-endian representation.
\item
  \(\texttt{dec\_scalar}(buf \in \bold{\Sigma}^{32})\): Interpret octet
  string \(buf\) as a little-endian integer. MUST output ``INVALID'' if
  the resulting value is \(\geq r\).
\item
  \(\texttt{enc\_point}(P \in \bold{G})\): Encodes a point in compressed
  form. The \(y\) coordinate is serialized in little-endian and the most
  significant bit of the last octet encodes the sign of the
  \(x\)-coordinate. This gives \texttt{ptLen} = \texttt{fLen} = \(32\).
\item
  \(\texttt{dec\_point}(buf \in \bold{\Sigma}^{32})\): Interpret octet
  string \(buf\) as a compressed point. Mask the sign bit from the last
  octet and interpret the result as a little-endian integer. MUST output
  ``INVALID'' if the resulting value is \(\geq q\). Otherwise,
  decompress the point and MUST output ``INVALID'' if it does not decode
  to a point on the prime subgroup \(\bold{G}\).
\item
  \(\texttt{dec\_scalar\_mod}(buf \in \bold{\Sigma}^*)\): Interpret
  octet string \(buf\) as a little-endian integer and reduce modulo the
  prime field order \(r\).
\item
  \(\texttt{enc\_64}(n \in \mathbb{N}_{2^{64}})\): Encode integer \(n\)
  as an 8-byte little-endian octet string.
\end{itemize}

Aggregate types (e.g.~proofs) MUST be encoded as the concatenation of
their individual fields in the order given by the structure definition,
without any separator.

\subsection{1.6. Procedures}\label{procedures}

\subsubsection{1.6.1. Transcript}\label{transcript}

The transcript provides a Fiat-Shamir transform with an absorb/squeeze
interface. Data is absorbed into an internal hash state; output bytes
are squeezed from it. After the first squeeze, \(\texttt{absorb}\) MUST
NOT be called.

\textbf{Abstract interface}:

\begin{itemize}
\tightlist
\item
  \(\texttt{new\_transcript}() \to T\): Create a fresh transcript
  instance and absorb \(\texttt{suite\_id}\).
\item
  \(\texttt{absorb}(data \in \bold{\Sigma}^*)\): Feed bytes into the
  hash state. MUST NOT be called after squeeze.
\item
  \(\texttt{squeeze}(n \in \mathbb{N}) \to \bold{\Sigma}^n\): Produce
  \(n\) output bytes.
\item
  \(\texttt{fork}() \to T\): Clone the transcript state.
\end{itemize}

A concrete instantiation using SHA-512 is given in Appendix A.1.

\subsubsection{1.6.2. VRF Input}\label{vrf-input}

The VRF input point \(I \in \bold{G}\) is derived from the input
octet-string using a \(\texttt{hash\_to\_curve}\) function that maps
arbitrary-length octet-strings to points in \(\bold{G}\).

\[I \gets \texttt{hash\_to\_curve}(i)\]

The function MUST behave as a random oracle: its output must be
indistinguishable from a uniformly random point in \(\bold{G}\), and the
discrete logarithm of the output with respect to any known base must be
unknown.

Verifiers MUST independently compute each \(I_i\) from the corresponding
input octet-string using the procedure above. Accepting prover-supplied
input points without recomputation breaks the VRF security guarantees,
and in the case of Thin VRF (section 3), enables trivial forgery.

A concrete instantiation using Elligator 2 is given in Appendix A.2.

\subsubsection{1.6.3. VRF Output}\label{vrf-output}

The VRF output point is generated from the VRF input point and secret
key scalar:

\[O \gets x \cdot I\]

The VRF output hash is a fixed-length octet string derived from the
output point using a transcript-based point-to-hash procedure. The
procedure is deliberately independent of the proof scheme: for a given
key and input, the output point \(O = x \cdot I\) is unique regardless
of whether Tiny VRF, Thin VRF, or Pedersen VRF is used to prove
correctness. The scheme determines how the proof is constructed, not the
VRF output itself. This separation allows applications to obtain
consistent output hashes across schemes for the same underlying
evaluation.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(O \in \bold{G}\): VRF output point.
\item
  \(N \in \mathbb{N}\): Desired output length in bytes. MUST be fixed
  per application context; \(N\) is not absorbed into the transcript, so
  \(\texttt{squeeze}(N_1)\) is a prefix of \(\texttt{squeeze}(N_2)\) for
  \(N_1 < N_2\).
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(o \in \bold{\Sigma}^N\): VRF output hash.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(T \gets \texttt{new\_transcript}()\)
\item
  \(T.\texttt{absorb}(\texttt{PointToHash} \;\Vert\; \texttt{enc\_point}(O))\)
\item
  \(o \gets T.\texttt{squeeze}(N)\)
\end{enumerate}

\textbf{Transcript}:

\begin{itemize}
\tightlist
\item
  \(T = \texttt{suite\_id} \;\Vert\; \texttt{PointToHash} \;\Vert\; \texttt{enc\_point}(O)\)
\end{itemize}

\subsubsection{1.6.4. Delinearization}\label{delinearization}

Merges input/output pairs into a single pair using delinearization
scalars derived from the transcript. For \(n = 0\), returns the identity
pair. For \(n = 1\), the pair is returned unchanged (\(z_0 = 1\)). For
\(n \geq 2\), random scalars prevent an attacker from mixing components
across pairs.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): Sequence of
  input/output pairs.
\item
  \(T\): Transcript state.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \((I_m, O_m) \in \bold{G}\times \bold{G}\): Merged input/output pair.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  If \(n = 0\): return \((\mathcal{O}, \mathcal{O})\)
\item
  \(T.\texttt{absorb}(\texttt{Delinearize})\)
\item
  \(z_0 \gets 1\)
\item
  For \(i = 1, \ldots, n-1\):
  \(z_i \gets \texttt{dec\_scalar\_mod}(T.\texttt{squeeze}(\texttt{challenge\_len}))\)
\item
  \(I_m \gets \sum_{i=0}^{n-1} z_i \cdot I_i,\ O_m \gets \sum_{i=0}^{n-1} z_i \cdot O_i\)
\item
  Return \((I_m, O_m)\)
\end{enumerate}

\textbf{Transcript} (where \(T_{in}\) is the caller-supplied state):

\begin{itemize}
\tightlist
\item
  \(T = T_{in} \;\Vert\; \texttt{Delinearize}\)
\end{itemize}

\subsubsection{1.6.5. VRF Transcript}\label{vrf-transcript}

Shared transcript construction used by all VRF-AD schemes. Absorbs
input/output pairs, merges them via delinearization (section 1.6.4), and
absorbs additional data.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(scheme\): Scheme identifier tag.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): Sequence of
  input/output pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(T\): Transcript state.
\item
  \((I_m, O_m) \in \bold{G}\times \bold{G}\): Merged input/output pair.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(T \gets \texttt{new\_transcript}()\)
\item
  \(T.\texttt{absorb}(scheme)\)
\item
  \(T.\texttt{absorb}(\texttt{enc\_64}(n))\)
\item
  For each \((I_i, O_i)\) in \(\overline{io}\):
  \(T.\texttt{absorb}(\texttt{enc\_point}(I_i) \;\Vert\; \texttt{enc\_point}(O_i))\)
\item
  \(T.\texttt{absorb}(\texttt{enc\_64}(\texttt{len}(ad)) \;\Vert\; ad)\)
\item
  \((I_m, O_m) \gets \texttt{delinearize}(\overline{io}, T.\texttt{fork}())\)
\item
  Return \((T, (I_m, O_m))\)
\end{enumerate}

\textbf{Transcript}:

\(\begin{aligned}
T = &\; \texttt{suite\_id} \;\Vert\; scheme \\
  &\; \Vert\; \texttt{enc\_64}(n) \;\Vert\; \texttt{enc\_point}(I_0) \;\Vert\; \texttt{enc\_point}(O_0) \;\Vert\; \cdots \;\Vert\; \texttt{enc\_point}(I_{n-1}) \;\Vert\; \texttt{enc\_point}(O_{n-1}) \\
  &\; \Vert\; \texttt{enc\_64}(\texttt{len}(ad)) \;\Vert\; ad
\end{aligned}\)

\subsubsection{1.6.6. Nonce}\label{nonce}

Deterministic nonce generation inspired by {[}RFC-8032{]} section 5.1.6.
The transcript carries shared state from \(\texttt{vrf\_transcript}\),
binding the nonce to the I/O pairs and additional data.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(d \in \bold{F}\): Secret scalar.
\item
  \(T\): Transcript state.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(k \in \bold{F}\): Nonce scalar.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(T' \gets T.\texttt{fork}()\)
\item
  \(T'.\texttt{absorb}(\texttt{NonceExpand} \;\Vert\; \texttt{enc\_scalar}(d))\)
\item
  \(h \gets T'.\texttt{squeeze}(64)\)
\item
  \(T.\texttt{absorb}(\texttt{Nonce} \;\Vert\; h)\)
\item
  \(k \gets \texttt{dec\_scalar\_mod}(T.\texttt{squeeze}(\text{expanded\_scalar\_len}))\)
\item
  If \(k = 0\): abort (implementation error; probability
  \(\approx 2^{-253}\)).
\end{enumerate}

\textbf{Transcript} (where \(T_{in}\) is the caller-supplied state):

\begin{itemize}
\tightlist
\item
  \(T' = T_{in} \;\Vert\; \texttt{NonceExpand} \;\Vert\; \texttt{enc\_scalar}(d)\)
\item
  \(T = T_{in} \;\Vert\; \texttt{Nonce} \;\Vert\; h\)
\end{itemize}

\subsubsection{1.6.7. Challenge}\label{challenge}

Derives a challenge scalar by absorbing curve points into the transcript
and squeezing.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(\bar{P} \in \bold{G}^m\): Sequence of \(m\) points.
\item
  \(T\): Transcript state.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(c \in \bold{F}\): Challenge scalar.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(T.\texttt{absorb}(\texttt{Challenge})\)
\item
  For each \(P_i\) in \(\bar{P}\):
  \(T.\texttt{absorb}(\texttt{enc\_point}(P_i))\)
\item
  \(c \gets \texttt{dec\_scalar\_mod}(T.\texttt{squeeze}(\texttt{challenge\_len}))\)
\end{enumerate}

\textbf{Transcript} (where \(T_{in}\) is the caller-supplied state):

\begin{itemize}
\tightlist
\item
  \(T = T_{in} \;\Vert\; \texttt{Challenge} \;\Vert\; \texttt{enc\_point}(P_0) \;\Vert\; \cdots \;\Vert\; \texttt{enc\_point}(P_{m-1})\)
\end{itemize}

\section{2. Tiny VRF}\label{tiny-vrf}

Compact VRF-AD scheme producing a short \((c, s)\) proof. Like Thin VRF,
it prepends the Schnorr pair \((G, Y)\) to the I/O list and proves a
single DLEQ on the delinearized merged pair. The challenge scalar \(c\)
is stored instead of the nonce commitment, yielding a smaller proof at
the cost of not supporting batch verification.

\textbf{Security}: VRF input points MUST be constructed via
hash-to-curve. If a prover knows \(d\) such that \(I = d \cdot G\), they
can forge arbitrary outputs for that input, because the delinearization
merges the Schnorr and VRF pairs into a single check that collapses when
all points are multiples of \(G\).

\textbf{Proof encoding}: The challenge \(c\) is produced by squeezing
\(\texttt{challenge\_len}\) bytes from the transcript. Since
\(2^{8 \cdot \texttt{challenge\_len}} < r\), no modular reduction occurs
and \(c\) is encoded as its raw \(\texttt{challenge\_len}\)-byte
little-endian representation. The scalar \(s\) is encoded via
\(\texttt{enc\_scalar}\) (32 bytes). The total proof size is
\(\texttt{challenge\_len} + 32\) bytes. Verifiers MUST reject proofs
where \(c \geq 2^{8 \cdot \texttt{challenge\_len}}\).

\subsection{2.1. Prove}\label{prove}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\pi = (c, s) \in (\bold{F}, \bold{F})\): Schnorr-like proof.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(Y \gets x \cdot G\)
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{TinyVrf}, [(G, Y)] \;\Vert\; \overline{io}, ad)\)
\item
  \(k \gets \texttt{nonce}(x, T.\texttt{fork}())\)
\item
  \(R \gets k \cdot I_m\)
\item
  \(c \gets \texttt{challenge}([R], T)\)
\item
  \(s \gets k + c \cdot x\)
\item
  \(\pi \gets (c, s)\)
\end{enumerate}

\subsection{2.2. Verify}\label{verify}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(Y \in \bold{G}\): Public key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\item
  \(\pi = (c, s) \in (\bold{F}, \bold{F})\): Schnorr-like proof.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Validate \(Y\) and all \(I_i, O_i\)
  \(\in \bold{G}\setminus \{\mathcal{O}\}\), output \(\bot\) if any is
  invalid or the identity.
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{TinyVrf}, [(G, Y)] \;\Vert\; \overline{io}, ad)\)
\item
  \(R \gets s \cdot I_m - c \cdot O_m\)
\item
  \(c' \gets \texttt{challenge}([R], T)\)
\item
  \(\theta \gets \top \text{ if } c = c' \text{ else } \bot\)
\end{enumerate}

\section{3. Thin VRF}\label{thin-vrf}

Thin VRF is structurally similar to Tiny VRF: it prepends \((G, Y)\) to
the I/O pairs, applies delinearization, and proves a single DLEQ on the
merged pair. The difference is the proof format: Thin VRF stores the
nonce commitment \(R\) rather than the challenge \(c\), which enables
batch verification at the cost of a slightly larger proof.

\subsection{3.1. Prove}\label{prove-1}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\pi = (R, s) \in (\bold{G}, \bold{F})\): Thin VRF proof.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(Y \gets x \cdot G\)
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{ThinVrf}, [(G, Y)] \;\Vert\; \overline{io}, ad)\)
\item
  \(k \gets \texttt{nonce}(x, T.\texttt{fork}())\)
\item
  \(R \gets k \cdot I_m\)
\item
  \(c \gets \texttt{challenge}([R], T)\)
\item
  \(s \gets k + c \cdot x\)
\item
  \(\pi \gets (R, s)\)
\end{enumerate}

\subsection{3.2. Verify}\label{verify-1}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(Y \in \bold{G}\): Public key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\item
  \(\pi = (R, s) \in (\bold{G}, \bold{F})\): Thin VRF proof.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Validate \(Y\), \(R\), and all \(I_i, O_i\)
  \(\in \bold{G}\setminus \{\mathcal{O}\}\), output \(\bot\) if any is
  invalid or the identity.
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{ThinVrf}, [(G, Y)] \;\Vert\; \overline{io}, ad)\)
\item
  \(c \gets \texttt{challenge}([R], T)\)
\item
  \(\theta \gets \top \text{ if } s \cdot I_m = R + c \cdot O_m \text{ else } \bot\)
\end{enumerate}

\subsection{3.3. Batch Verify}\label{batch-verify}

Multiple Thin VRF proofs can be verified together by combining the
individual verification equations with random weights (Schwartz-Zippel
lemma).

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  For \(j = 0, \ldots, N-1\): a tuple
  \((Y_j, \overline{io}_j, ad_j, \pi_j)\) where:

  \begin{itemize}
  \tightlist
  \item
    \(Y_j \in \bold{G}\): Public key.
  \item
    \(\overline{io}_j \in (\bold{G}\times \bold{G})^{M_j}\): VRF
    input/output pairs.
  \item
    \(ad_j \in \bold{\Sigma}^*\): Additional data octet-string.
  \item
    \(\pi_j = (R_j, s_j) \in (\bold{G}, \bold{F})\): Thin VRF proof.
  \end{itemize}
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if all proofs verify,
  \(\bot\) otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  For each proof \(j\):

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Validate \(Y_j\), \(R_j\), and all \(I_{j,i}, O_{j,i}\)
    \(\in \bold{G}\setminus \{\mathcal{O}\}\), output \(\bot\) if any is
    invalid or the identity.
  \item
    \((T_j, (I_{m,j}, O_{m,j})) \gets \texttt{vrf\_transcript}(\texttt{ThinVrf}, [(G, Y_j)] \;\Vert\; \overline{io}_j, ad_j)\)
  \item
    \(c_j \gets \texttt{challenge}([R_j], T_j)\)
  \end{enumerate}
\item
  Derive random weights:

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    \(T_w \gets \texttt{new\_transcript}()\)
  \item
    \(T_w.\texttt{absorb}(\texttt{BatchVerify})\)
  \item
    For each \(j\):
    \(T_w.\texttt{absorb}(\texttt{enc\_scalar}(c_j) \;\Vert\; \texttt{enc\_scalar}(s_j))\)
  \end{enumerate}
\item
  Check the combined equation:
  \[\sum_{j=0}^{N-1} w_j \cdot (s_j \cdot I_{m,j} - R_j - c_j \cdot O_{m,j}) = \mathcal{O}\]
  where
  \(w_j \gets \texttt{dec\_scalar\_mod}(T_w.\texttt{squeeze}(\texttt{challenge\_len}))\).
\end{enumerate}

\textbf{Transcript}:

\(\begin{aligned}
T_w = &\; \texttt{suite\_id} \;\Vert\; \texttt{BatchVerify} \\
  &\; \Vert\; \texttt{enc\_scalar}(c_0) \;\Vert\; \texttt{enc\_scalar}(s_0) \;\Vert\; \cdots \;\Vert\; \texttt{enc\_scalar}(c_{N-1}) \;\Vert\; \texttt{enc\_scalar}(s_{N-1})
\end{aligned}\)

\section{4. Pedersen VRF}\label{pedersen-vrf}

Pedersen VRF resembles Tiny VRF but replaces the public key with a
Pedersen commitment to the secret key, which makes this VRF useful in
anonymized ring proofs.

The scheme proves that the output has been generated with a secret key
associated with a blinded public key (instead of the public key). The
blinded public key is a cryptographic commitment to the public key, and
it can be unblinded to prove that the output of the VRF corresponds to
the public key of the signer.

This specification mostly follows the design proposed by
\href{https://eprint.iacr.org/2023/002}{BCHSV23} {[}2{]} in section 4
with some details about blinding base point value and challenge
generation procedure.

The \emph{blinding base} \(B \in \bold{G}\) is defined as:
\[\footnotesize\begin{aligned}
x &= 23335687741101763108036518445642207119627658113885888016488710494487028845889 \\
y &= 5552214580375038693022409684979828600325210968745774080859660443337357929963
\end{aligned}\]

A point with unknown discrete logarithm derived using the
\texttt{hash\_to\_curve} function as described in Appendix A.2 with
input the string: \texttt{"pedersen-blinding"}.

\subsection{4.1. Prove}\label{prove-2}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\pi = (\bar{Y}, R, O_k, s, s_b) \in (\bold{G}, \bold{G}, \bold{G}, \bold{F}, \bold{F})\):
  Pedersen proof.
\item
  \(b \in \bold{F}\): Blinding factor.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{PedersenVrf}, \overline{io}, ad)\)
\item
  \(b \gets \texttt{blinding}(x, T.\texttt{fork}())\) (see Appendix A.4)
\item
  \(\bar{Y} \gets x \cdot G + b \cdot B\)
\item
  \(T.\texttt{absorb}(\texttt{enc\_point}(\bar{Y}))\)
\item
  \(k \gets \texttt{nonce}(x, T.\texttt{fork}())\),
  \(\quad k_b \gets \texttt{nonce}(b, T.\texttt{fork}())\)
\item
  \(R \gets k \cdot G + k_b \cdot B\)
\item
  \(O_k \gets k \cdot I_m\)
\item
  \(c \gets \texttt{challenge}([R, O_k], T)\)
\item
  \(s \gets k + c \cdot x\), \(\quad s_b \gets k_b + c \cdot b\)
\item
  \(\pi \gets (\bar{Y}, R, O_k, s, s_b)\)
\end{enumerate}

\subsection{4.2. Verify}\label{verify-2}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\item
  \(\pi = (\bar{Y}, R, O_k, s, s_b) \in (\bold{G}, \bold{G}, \bold{G}, \bold{F}, \bold{F})\):
  Pedersen proof.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Validate \(\bar{Y}\), \(R\), \(O_k\), and all \(I_i, O_i\)
  \(\in \bold{G}\setminus \{\mathcal{O}\}\), output \(\bot\) if any is
  invalid or the identity.
\item
  \((T, (I_m, O_m)) \gets \texttt{vrf\_transcript}(\texttt{PedersenVrf}, \overline{io}, ad)\)
\item
  \(T.\texttt{absorb}(\texttt{enc\_point}(\bar{Y}))\)
\item
  \(c \gets \texttt{challenge}([R, O_k], T)\)
\item
  \(\theta_0 \gets \top \text{ if } O_k + c \cdot O_m = s \cdot I_m \text{ else } \bot\)
\item
  \(\theta_1 \gets \top \text{ if } R + c \cdot \bar{Y} = s \cdot G + s_b \cdot B \text{ else } \bot\)
\item
  \(\theta = \theta_0 \land \theta_1\)
\end{enumerate}

Note: no public key appears in the verify inputs -- verification uses
the committed key \(\bar{Y}\) from the proof.

\subsection{4.3. Unblinding}\label{unblinding}

To link a Pedersen VRF proof to a specific public key, the prover
reveals the blinding factor \(b\) and the verifier checks:

\[\bar{Y} = Y + b \cdot B\]

where \(Y \in \bold{G}\setminus \{\mathcal{O}\}\) is the claimed public
key. The verifier MUST validate \(Y\) before accepting the association.

\subsection{4.4. Batch Verify}\label{batch-verify-1}

Multiple Pedersen VRF proofs can be verified together by combining the
individual verification equations with random weights (Schwartz-Zippel
lemma). Each proof contributes two equations (VRF correctness and
Pedersen commitment correctness), each weighted by an independent random
scalar.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  For \(j = 0, \ldots, N-1\): a tuple \((\overline{io}_j, ad_j, \pi_j)\)
  where:

  \begin{itemize}
  \tightlist
  \item
    \(\overline{io}_j \in (\bold{G}\times \bold{G})^{M_j}\): VRF
    input/output pairs.
  \item
    \(ad_j \in \bold{\Sigma}^*\): Additional data octet-string.
  \item
    \(\pi_j = (\bar{Y}_j, R_j, O_{k,j}, s_j, s_{b,j}) \in (\bold{G}, \bold{G}, \bold{G}, \bold{F}, \bold{F})\):
    Pedersen proof.
  \end{itemize}
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if all proofs verify,
  \(\bot\) otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  For each proof \(j\):

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Validate \(\bar{Y}_j\), \(R_j\), \(O_{k,j}\), and all
    \(I_{j,i}, O_{j,i}\) \(\in \bold{G}\setminus \{\mathcal{O}\}\),
    output \(\bot\) if any is invalid or the identity.
  \item
    \((T_j, (I_{m,j}, O_{m,j})) \gets \texttt{vrf\_transcript}(\texttt{PedersenVrf}, \overline{io}_j, ad_j)\)
  \item
    \(T_j.\texttt{absorb}(\texttt{enc\_point}(\bar{Y}_j))\)
  \item
    \(c_j \gets \texttt{challenge}([R_j, O_{k,j}], T_j)\)
  \end{enumerate}
\item
  Derive random weights:

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    \(T_w \gets \texttt{new\_transcript}()\)
  \item
    \(T_w.\texttt{absorb}(\texttt{BatchVerify})\)
  \item
    For each \(j\):
    \(T_w.\texttt{absorb}(\texttt{enc\_scalar}(c_j) \;\Vert\; \texttt{enc\_scalar}(s_j) \;\Vert\; \texttt{enc\_scalar}(s_{b,j}))\)
  \end{enumerate}
\item
  Check the combined equations:
  \[\sum_{j=0}^{N-1} t_j \cdot (O_{k,j} + c_j \cdot O_{m,j} - s_j \cdot I_{m,j}) + u_j \cdot (R_j + c_j \cdot \bar{Y}_j - s_j \cdot G - s_{b,j} \cdot B) = \mathcal{O}\]
  where:

  \begin{itemize}
  \tightlist
  \item
    \(t_j \gets \texttt{dec\_scalar\_mod}(T_w.\texttt{squeeze}(\texttt{challenge\_len}))\)
  \item
    \(u_j \gets \texttt{dec\_scalar\_mod}(T_w.\texttt{squeeze}(\texttt{challenge\_len}))\)
  \end{itemize}
\end{enumerate}

\textbf{Transcript}:

\(\begin{aligned}
T_w = &\; \texttt{suite\_id} \;\Vert\; \texttt{BatchVerify} \\
  &\; \Vert\; \texttt{enc\_scalar}(c_0) \;\Vert\; \texttt{enc\_scalar}(s_0) \;\Vert\; \texttt{enc\_scalar}(s_{b,0}) \\
  &\; \Vert\; \cdots \\
  &\; \Vert\; \texttt{enc\_scalar}(c_{N-1}) \;\Vert\; \texttt{enc\_scalar}(s_{N-1}) \;\Vert\; \texttt{enc\_scalar}(s_{b,N-1})
\end{aligned}\)

\section{5. Ring VRF}\label{ring-vrf}

Anonymized ring VRF based on Pedersen VRF (section 4) and Ring Proof as
proposed in \href{https://eprint.iacr.org/2023/002}{BCHSV23} {[}2{]}.

The ring proof can be seen as a special case of the Committee Key Scheme
(CKS) introduced by \href{https://eprint.iacr.org/2022/1205}{CSSV22}
{[}3{]}, reduced to a single signer. In CKS, a prover commits to a set
of public keys using a KZG polynomial commitment and produces a SNARK
showing that a subset of keys -- identified by a bitvector -- belongs to
the committed set. The ring proof is the degenerate case where the
bitvector has exactly one bit set: it proves that a single (blinded) key
is a member of the committed ring, without revealing which one.

The concrete specification of the ring proof scheme is given in
\href{https://github.com/davxy/ring-proof-spec}{VG24} {[}5{]}. The
following configuration specializes it for this scheme:

\begin{itemize}
\tightlist
\item
  \textbf{Groups and Fields}:

  \begin{itemize}
  \tightlist
  \item
    \(\mathbb{G_1}\): BLS12-381 prime order subgroup.
  \item
    \(\mathbb{F}\): BLS12-381 scalar field.
  \item
    \(J\): Bandersnatch curve defined over \(\mathbb{F}\).
  \end{itemize}
\item
  \textbf{Polynomial Commitment Scheme}

  \begin{itemize}
  \tightlist
  \item
    KZG with SRS derived from
    \href{https://zfnd.org/conclusion-of-the-powers-of-tau-ceremony}{Zcash}
    powers of tau ceremony.
  \end{itemize}
\item
  \textbf{Fiat-Shamir Transform}

  \begin{itemize}
  \tightlist
  \item
    \href{https://crates.io/crates/ark-transcript}{\texttt{ark-transcript}}.
  \item
    Begin with empty transcript and ``ring-proof'' label.
  \item
    Push \(R\) to the transcript after instancing.
  \end{itemize}
\item
  Accumulator base point \(S \in \bold{G}\) is defined as:
  \[\footnotesize\begin{aligned}
  x &= 14056632001415368875257708737821299882600475929746323097150942355715730684350 \\
  y &= 10322661992765989500407719465917595459409463902187386706652408883505670839210
  \end{aligned}\]
\end{itemize}

A point with unknown discrete logarithm derived using the
\texttt{hash\_to\_curve} function as described in Appendix A.2 with
input the string: \texttt{"ring-accumulator"}.

\begin{itemize}
\tightlist
\item
  Padding point \(\square \in \bold{G}\) is defined as:
  \[\footnotesize\begin{aligned}
  x &= 26913883415342152801331916189968962157924271221160514298872262294143390094043 \\
  y &= 30874728313203001508631936119690348239461579770372782660098261717479009115354
  \end{aligned}\]
\end{itemize}

A point with unknown discrete logarithm derived using the
\texttt{hash\_to\_curve} function as described in Appendix A.2 with
input the string: \texttt{"ring-padding"}.

\begin{itemize}
\item
  Polynomials domain (\(\langle \omega \rangle = \mathbb{D}\))
  generator:
  \[\footnotesize \omega = 49307615728544765012166121802278658070711169839041683575071795236746050763237\]
\item
  \(|\mathbb{D}| = 2048\)
\end{itemize}

\subsection{5.1. Prove}\label{prove-3}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret key.
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\item
  \(P\): Ring prover (encapsulates ring keys and prover index).
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\pi_p \in (\bold{G}, \bold{G}, \bold{G}, \bold{F}, \bold{F})\):
  Pedersen proof.
\item
  \(\pi_r \in ((G_1)^4, (\bold{F})^7, G_1, \bold{F}, G_1, G_1)\): Ring
  proof.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \((\pi_p, b) \gets Pedersen.prove(x, \overline{io}, ad)\)
\item
  \(\pi_r \gets Ring.prove(P, b)\)
\end{enumerate}

The blinding factor \(b\) is derived internally by Pedersen prove
(section 4.1, step 2) and forwarded to the ring prover. \(Ring.prove\)
and \(Ring.verify\) are defined in
\href{https://github.com/davxy/ring-proof-spec}{VG24} {[}5{]}.

\subsection{5.2. Verify}\label{verify-3}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(\overline{io} \in (\bold{G}\times \bold{G})^n\): VRF input/output
  pairs.
\item
  \(ad \in \bold{\Sigma}^*\): Additional data octet-string.
\item
  \(\pi_p \in (\bold{G}, \bold{G}, \bold{G}, \bold{F}, \bold{F})\):
  Pedersen proof.
\item
  \(\pi_r \in ((G_1)^4, (\bold{F})^7, G_1, \bold{F}, G_1, G_1)\): Ring
  proof.
\item
  \(V \in (G_1)^3\): Ring verifier (pre-processed commitment).
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(\theta_0 \gets Pedersen.verify(\overline{io}, ad, \pi_p)\)
\item
  \((\bar{Y}, R, O_k, s, s_b) \gets \pi_p\)
\item
  \(\theta_1 \gets Ring.verify(V, \pi_r, \bar{Y})\)
\item
  \(\theta \gets \theta_0 \land \theta_1\)
\end{enumerate}

\section{Appendix A. Concrete
Instantiations}\label{appendix-a.-concrete-instantiations}

The following are concrete instantiations of the abstract interfaces
defined in the main specification. They are provided to enable
interoperable implementations and reproducible test vectors. Alternative
constructions that satisfy the same security requirements are equally
valid.

\subsection{A.1. Transcript
Construction}\label{a.1.-transcript-construction}

Instantiation of the transcript interface (section 1.6.1) using SHA-512.

\textbf{Initialization}: \(\texttt{new\_transcript}()\) creates a fresh
SHA-512 state and feeds \(\texttt{suite\_id}\) into it.

\textbf{Absorb}: feeds raw bytes directly into the SHA-512 state.
Consecutive absorb calls are equivalent to a single absorb of the
concatenated data. This is safe because all protocol fields use
fixed-width encoding (\(\texttt{enc\_point}\): 32 bytes,
\(\texttt{enc\_scalar}\): 32 bytes, \(\texttt{enc\_64}\): 8 bytes,
domain tags: 1 byte) or explicit length prefixing (\(ad\) via
\(\texttt{enc\_64}(\texttt{len}(ad)) \;\Vert\; ad\)), so the byte stream
is unambiguous given the inputs agreed upon by both parties.

\textbf{Squeeze} (counter-mode XOF): on the first squeeze call, finalize
the SHA-512 state to obtain a 64-byte \(seed\). Then produce output
blocks:

\[block_i = \text{SHA-512}(seed \;\Vert\; \texttt{enc\_64}(i)) \quad \text{for } i = 0, 1, 2, \ldots\]

where \(\texttt{enc\_64}(n)\) encodes integer \(n\) as an 8-byte
little-endian octet string. Each block yields 64 bytes. Output is read
sequentially across blocks; partial block state is preserved between
squeeze calls.

\textbf{Fork}: duplicates the full internal state (including any partial
block position if squeezing has begun).

\subsection{A.2. Hash to Curve}\label{a.2.-hash-to-curve}

Instantiation of the \(\texttt{hash\_to\_curve}\) function (section
1.6.2) using the method defined in section 3 of
\href{https://datatracker.ietf.org/doc/rfc9380}{RFC-9380} {[}6{]}, with
the \emph{Elligator 2} map to curve (section 6.8.2) and
\(\texttt{expand\_message\_xmd}\) with SHA-512 (section 5.3.1).

This is the random oracle (\texttt{\_RO\_}) construction: the input is
hashed to two independent field elements, each is mapped to a curve
point via Elligator 2, and the results are added.

\[I \gets \texttt{hash\_to\_curve\_ell2}(DST, i)\]

The domain separation tag is:

\[DST = \texttt{suite\_id} \;\Vert\; \texttt{HashToCurve}\]

i.e.~the 27-byte \(\texttt{suite\_id}\) string concatenated with the
single \(\texttt{HashToCurve}\) tag byte (0x60). This matches the
per-operation tagging used elsewhere in the protocol.

\subsection{A.3. Secret Key
Generation}\label{a.3.-secret-key-generation}

Derives a secret scalar from a 32-byte seed.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(seed \in \bold{\Sigma}^{32}\): seed octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): secret key scalar.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(i \gets 0\)
\item
  \(T \gets \texttt{new\_transcript}()\)
\item
  \(T.\texttt{absorb}(seed)\)
\item
  If \(i > 0\): \(T.\texttt{absorb}(i)\) where \(i\) is encoded as a
  single octet
\item
  \(d \gets \texttt{dec\_scalar\_mod}(seed)\)
\item
  \(x \gets \texttt{nonce}(d, T)\)
\item
  If \(x = 0\): increment \(i\) and go to step 2
\item
  Return \(x\)
\end{enumerate}

The seed is absorbed into the transcript and also passed as a scalar to
the \(\texttt{nonce}\) procedure (section 1.6.6), ensuring seed entropy
flows through both the transcript state and the secret scalar input
paths.

\subsection{A.4. Blinding Factor
Generation}\label{a.4.-blinding-factor-generation}

Generates the Pedersen VRF blinding factor deterministically from the
secret key and the VRF transcript state, using the nonce function
(section 1.6.6) with a distinct domain separator.

\textbf{Linkability warning}: because \(b\) is derived deterministically
from \((x, T)\), two Pedersen VRF proofs with the same secret key, I/O
pairs, and additional data will produce the same blinding factor \(b\)
and therefore the same blinded public key
\(\bar{Y} = x \cdot G + b \cdot B\). An observer can detect that both
proofs originate from the same signer by comparing \(\bar{Y}\) values.
Applications that require unlinkability across repeated proofs on the
same inputs should generate \(b\) as a fresh uniformly random scalar
rather than using this deterministic method.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \bold{F}\): Secret scalar.
\item
  \(T\): Transcript state (from \(\texttt{vrf\_transcript}\)).
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(b \in \bold{F}\): Blinding factor scalar.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(T.\texttt{absorb}(\texttt{PedersenBlinding})\)
\item
  \(b \gets \texttt{nonce}(x, T)\)
\end{enumerate}

\section{Appendix B. Behavior with Zero I/O
Pairs}\label{appendix-b.-behavior-with-zero-io-pairs}

When \(n = 0\) no VRF output can be derived, since there are no output
points to hash. The proof-of-knowledge component, however, remains sound
in all schemes: a valid proof still requires knowledge of the secret key
\(x\).

\begin{itemize}
\item
  \textbf{Tiny VRF and Thin VRF}: Both schemes prepend the Schnorr pair
  \((G, Y)\) to the I/O list before delinearization (sections 2.1 and
  3.1, step 2), so the internal pair count is at least 1 regardless of
  the user-supplied \(n\). With zero VRF pairs, the scheme degenerates
  to a Schnorr signature on the additional data \(ad\), proving
  knowledge of \(x\) for public key \(Y\).
\item
  \textbf{Pedersen VRF}: No Schnorr pair is prepended, so with \(n = 0\)
  the \(\texttt{delinearize}\) procedure (section 1.6.4) sets the merged
  pair to the identity: \((I_m, O_m) = (\mathcal{O}, \mathcal{O})\). The
  VRF output check \(O_k + c \cdot O_m = s \cdot I_m\) is vacuously
  satisfied (\(\mathcal{O} = \mathcal{O}\)), but the commitment check
  \(R + c \cdot \bar{Y} = s \cdot G + s_b \cdot B\) still proves
  knowledge of the Pedersen commitment opening \((x, b)\).
\end{itemize}

\section{Appendix C. Test Vectors}\label{appendix-c.-test-vectors}

The test vectors in this section were generated using \texttt{ark-vrf}
libraries revision \texttt{b22ae6d}.

\subsection{C.1. Tiny VRF Test
Vectors}\label{c.1.-tiny-vrf-test-vectors}

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
proof_c: Proof 'c' component,
proof_s: Proof 's' component,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-1}\label{bandersnatch_sha-512_ell2_tiny---vector-1}

\begin{verbatim}
c9922b7a9849b9928e15c655dd2f22ceef737cc355024f43d4b04bf4398c270d,
5a538209ff1fc7b1c9c8e1da05b3e169acf10a8b1591b3af029fe4eede0bbc71,
-,
-,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
54421f7ffc399872f1cb868efbb7eef4034178f1e369cebfb964ca61e4f3f256,
7b89f2aba6af7474694f24f75adf48336e00dcc8f3ac889ef4daa53c859497a6,
5685489f948058d1ac34ffc87d6adc09,
be881519a8790c307e3997b9b7905061b82009bc9d73ee5c5363319b1c884915,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-2}\label{bandersnatch_sha-512_ell2_tiny---vector-2}

\begin{verbatim}
0b4259ca1b10c9ed462532639113e1caf26b3a1a2d9e91ecef2fc5c2d23aed0a,
ff341f0c9da793b2d8fef91bcbfd5b55c2185352e4289edc1dd6c64e3fe09b0d,
0a,
-,
8ec04d55a790d47cd32c5062cb44517f164515dac88a8ea6d972db1a7da08abf,
e20e48a14d1ab23cad04e8bc39705d194e87587072fe2e7114d1f85fd7fb6105,
f7f5da876f037509854307d89273b14ef5db4f0971df0879963e1bf0e775636f,
8d56976c451b512a88a28704cd62546e,
68a6a31d6ce21ac9ea4e6eb688e19e08fc30a50a0dcd7c459dc0be49daaad415,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-3}\label{bandersnatch_sha-512_ell2_tiny---vector-3}

\begin{verbatim}
dd60163595ff312a49aa5849917ba19020038ccd42f8a1d468da0973079bdb15,
fbba8feb488e767b9864726fffdc8595896757430eba9162a1a5d9a03381d5a4,
-,
0b8c,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
719ace6342e2c5b3615e33d6e081c6ffbf0813f3f42ccbdf92973869fab0bbe5,
cc87c37551a222fe1207655f20225cb79a3dc2ebcefd7111550911e36423ad62,
7d7a08eed618b81bef1ca85695b93d6d,
3a1107ff4361fd10bf5b891d5554cc76e56502d9f034e921eb2cac0aa73d9206,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-4}\label{bandersnatch_sha-512_ell2_tiny---vector-4}

\begin{verbatim}
dfc32f03fe9487f123f2afeeb9487cb6b1eb23efac24a60ae540f5aa632ddd18,
f8487052801a89161424ee745189b5f7fe568819b9f13f44a8b3d173b57e928a,
73616d706c65,
-,
fa6a45172b622ddaccbcf7a3b2d91a36ba504598a83d5a4ed23b416063e4e039,
8f3ee5f3e386775c13093f84678e01594419d747a7037619fa7ea20790044218,
67c6fbdf10f3b5abec5c5ea368662455aa1cac36a6a17621ddb2b526c52fd8dc,
e44e5064895730cb04907d46262e63fa,
393f12e07c2ce66c08855bcf64a9c3b1dc29e455af7e235500f04076edb0c70e,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-5}\label{bandersnatch_sha-512_ell2_tiny---vector-5}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
-,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
c43dfc9ad3e72ab427810f5879683725,
08484f31d398c8f27b8ff363354bb14a5b5c23caf1436b321f5ea30b7f555e13,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-6}\label{bandersnatch_sha-512_ell2_tiny---vector-6}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
53613c4e23191e4bc2632927f7fd4316,
84e4072747518ad201335c841fac19222f8ee895f288da6304cd89b3ab4c7708,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_tiny -
vector-7}\label{bandersnatch_sha-512_ell2_tiny---vector-7}

\begin{verbatim}
9504efbeadf81b20a9cb64c1331915eb3718a574227458230d1d80dfa94e8b13,
704fd3784947de4db4fdcf0b477530d094bf5a656707b7d6cb43edbc4db7336b,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
1617b4fca3d7354fd43ae783bd6d0cfc526a80e257fcccfdf8e4d87e74dd7c6d,
6b279b85a1c55f55db80167e6bee997a5bf25c1767ffc2a34ae696baf606f5a0,
365b235ddb44510f484f14d5d19a1cd6,
9f5f9515507c84924f87b5cf549da8b177879cd2f835f94b91e36543e0cfbb0c,
\end{verbatim}

\subsection{C.2. Thin VRF Test
Vectors}\label{c.2.-thin-vrf-test-vectors}

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
proof_r: Proof 'r' component,
proof_s: Proof 's' component,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-1}\label{bandersnatch_sha-512_ell2_thin---vector-1}

\begin{verbatim}
c9922b7a9849b9928e15c655dd2f22ceef737cc355024f43d4b04bf4398c270d,
5a538209ff1fc7b1c9c8e1da05b3e169acf10a8b1591b3af029fe4eede0bbc71,
-,
-,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
54421f7ffc399872f1cb868efbb7eef4034178f1e369cebfb964ca61e4f3f256,
7b89f2aba6af7474694f24f75adf48336e00dcc8f3ac889ef4daa53c859497a6,
d969c67f8fd97fcc8c0f8b129810ef5427786e319e304a056038caf32286d15e,
374e93cc0df1aaa3cbe7a66397213275e852717462f8a9b775ed8bcb68f45b00,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-2}\label{bandersnatch_sha-512_ell2_thin---vector-2}

\begin{verbatim}
0b4259ca1b10c9ed462532639113e1caf26b3a1a2d9e91ecef2fc5c2d23aed0a,
ff341f0c9da793b2d8fef91bcbfd5b55c2185352e4289edc1dd6c64e3fe09b0d,
0a,
-,
8ec04d55a790d47cd32c5062cb44517f164515dac88a8ea6d972db1a7da08abf,
e20e48a14d1ab23cad04e8bc39705d194e87587072fe2e7114d1f85fd7fb6105,
f7f5da876f037509854307d89273b14ef5db4f0971df0879963e1bf0e775636f,
22be463a480dfadb3beb93ba75890a612fb65e206fecdd9fa9ec130ed16db268,
2eb15dc87c37022290606c34db23fdd7a80648e6aa0dce076ca3694000a72c01,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-3}\label{bandersnatch_sha-512_ell2_thin---vector-3}

\begin{verbatim}
dd60163595ff312a49aa5849917ba19020038ccd42f8a1d468da0973079bdb15,
fbba8feb488e767b9864726fffdc8595896757430eba9162a1a5d9a03381d5a4,
-,
0b8c,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
719ace6342e2c5b3615e33d6e081c6ffbf0813f3f42ccbdf92973869fab0bbe5,
cc87c37551a222fe1207655f20225cb79a3dc2ebcefd7111550911e36423ad62,
2d726da5bc791c511e7b5629bde266151d66f9f36d276dbe16dc1c900f4913dd,
743aaadff73eaaccc8e6cc333542faa331a132012e9cb2112a1e681546152d01,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-4}\label{bandersnatch_sha-512_ell2_thin---vector-4}

\begin{verbatim}
dfc32f03fe9487f123f2afeeb9487cb6b1eb23efac24a60ae540f5aa632ddd18,
f8487052801a89161424ee745189b5f7fe568819b9f13f44a8b3d173b57e928a,
73616d706c65,
-,
fa6a45172b622ddaccbcf7a3b2d91a36ba504598a83d5a4ed23b416063e4e039,
8f3ee5f3e386775c13093f84678e01594419d747a7037619fa7ea20790044218,
67c6fbdf10f3b5abec5c5ea368662455aa1cac36a6a17621ddb2b526c52fd8dc,
9a638cee379161ecf1a9269801631303359a531b035076369617c42ef46afcb1,
223446d4fd1450c1fef095c3fd3d5a52ae9f3a8b07a88d7e7ddaed089b235504,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-5}\label{bandersnatch_sha-512_ell2_thin---vector-5}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
-,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
fdfae23d8d8c9a5225a7bd49b65cc276abf7ce0f48a3730ca74eb57fe0b27467,
d55860b9c11a56cbe92b5d9c992fd95756fe1845be0be7eaa2a291b524cd111a,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-6}\label{bandersnatch_sha-512_ell2_thin---vector-6}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
d415fcd6eff582440fab9c62819b3bb82dd7158a2faf0465512aa095e9e885c2,
f2f59942f122f9566576ff9cfffbc803f1229881044aa69cca96193106b08c0c,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_thin -
vector-7}\label{bandersnatch_sha-512_ell2_thin---vector-7}

\begin{verbatim}
9504efbeadf81b20a9cb64c1331915eb3718a574227458230d1d80dfa94e8b13,
704fd3784947de4db4fdcf0b477530d094bf5a656707b7d6cb43edbc4db7336b,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
1617b4fca3d7354fd43ae783bd6d0cfc526a80e257fcccfdf8e4d87e74dd7c6d,
6b279b85a1c55f55db80167e6bee997a5bf25c1767ffc2a34ae696baf606f5a0,
9f9f6670d06734e319a01c6afb72e0e3647085dae2216c707a22643a3ef1a5c2,
74544f931a955eb7f38dab224988f37425b1275b78ed4340f6d5b7c4bc91a60a,
\end{verbatim}

\subsection{C.3. Pedersen VRF Test
Vectors}\label{c.3.-pedersen-vrf-test-vectors}

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
blinding: Blinding factor,
proof_pk_com (Y^-): Public key commitment,
proof_r: Proof 'R' component,
proof_ok: Proof 'O_k' component,
proof_s: Proof 's' component,
proof_sb: Proof 's_b' component
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-1}\label{bandersnatch_sha-512_ell2_pedersen---vector-1}

\begin{verbatim}
c9922b7a9849b9928e15c655dd2f22ceef737cc355024f43d4b04bf4398c270d,
5a538209ff1fc7b1c9c8e1da05b3e169acf10a8b1591b3af029fe4eede0bbc71,
-,
-,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
54421f7ffc399872f1cb868efbb7eef4034178f1e369cebfb964ca61e4f3f256,
7b89f2aba6af7474694f24f75adf48336e00dcc8f3ac889ef4daa53c859497a6,
afa1000852c300cbf235a6955ec4105b01919fa67ec6cc92ec92100f19c25809,
680539c070ebcaca50c4bf201869c2c355f1467e1b8ece6e0bcafc466872c5cf,
375a8ec2e95f58a41ea09090f9560e580e7a3cc67998129fa98dac1da5d0850e,
5071efbef9428b2a26eb09440891c6829bc0c57b4254ca811ce453a0d5938dea,
7dc8aa043b28383d334ef500fd7d770d35ab1c5ebc28df0807215911f4ab2d10,
045343af67f88d35679beab125c38b80029099b746ea47ef3eb488b1d38d130d,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-2}\label{bandersnatch_sha-512_ell2_pedersen---vector-2}

\begin{verbatim}
0b4259ca1b10c9ed462532639113e1caf26b3a1a2d9e91ecef2fc5c2d23aed0a,
ff341f0c9da793b2d8fef91bcbfd5b55c2185352e4289edc1dd6c64e3fe09b0d,
0a,
-,
8ec04d55a790d47cd32c5062cb44517f164515dac88a8ea6d972db1a7da08abf,
e20e48a14d1ab23cad04e8bc39705d194e87587072fe2e7114d1f85fd7fb6105,
f7f5da876f037509854307d89273b14ef5db4f0971df0879963e1bf0e775636f,
da3304d52c2a64ea75504ac44776e5e4900a38eb9a61f9478285aeccba6ec41c,
a356a2fafe785bc79860ef65534df7c1a2ee7d45ff6db649537dac1687ae4785,
ec546c1932f72e146a0e45d7107c97e99aacc9c72fd6ae6fd0b0417124aa26ca,
1d661c6349b33182ec77b58457f6d45dd9a618017ea021b986cf1eff18c4ef95,
1e8eb9a8cf017c6a50d0f947f9bf02575b60c714c81602a8f06965ec7e67c300,
49c44ad19ea4aaadfc98c2586660dbf3d8a434bb062fa948d82fd4a717ac5f12,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-3}\label{bandersnatch_sha-512_ell2_pedersen---vector-3}

\begin{verbatim}
dd60163595ff312a49aa5849917ba19020038ccd42f8a1d468da0973079bdb15,
fbba8feb488e767b9864726fffdc8595896757430eba9162a1a5d9a03381d5a4,
-,
0b8c,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
719ace6342e2c5b3615e33d6e081c6ffbf0813f3f42ccbdf92973869fab0bbe5,
cc87c37551a222fe1207655f20225cb79a3dc2ebcefd7111550911e36423ad62,
3dd321bf1fbbafd76d48c000a28768152e919789bd57cd50d5e17c88a1baec0a,
6d16e2ff7b28a8880499e34cfe6ffbb1d12efc27675af3fef635e8761c893dee,
5311bd0755a2bbc6db01b930526e85120af5189e2fb259fc941f3acb1611d6eb,
3c4ea965693b470b0da4f9c9508da97dfa70e5e85ee78fbd3af377a2298b4864,
a48a2f80da4190ec19e293a50bbc1bc047ebc38a14f4f19f97f5daec48ab4205,
eb91c85fb3b211f1ec63612950d04c78fc19a760294d01bd82f9218e944b640d,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-4}\label{bandersnatch_sha-512_ell2_pedersen---vector-4}

\begin{verbatim}
dfc32f03fe9487f123f2afeeb9487cb6b1eb23efac24a60ae540f5aa632ddd18,
f8487052801a89161424ee745189b5f7fe568819b9f13f44a8b3d173b57e928a,
73616d706c65,
-,
fa6a45172b622ddaccbcf7a3b2d91a36ba504598a83d5a4ed23b416063e4e039,
8f3ee5f3e386775c13093f84678e01594419d747a7037619fa7ea20790044218,
67c6fbdf10f3b5abec5c5ea368662455aa1cac36a6a17621ddb2b526c52fd8dc,
b3f08962012e4f4aa9e6482d7d682275ac98e57f099b991947fad5a53451d51b,
1c48e5ce0ae9b3e7a09626bc1333544f1dbe5033d5efd591a059b04a41830eb6,
17b630103915e544c1b4b1a3e8cbad9cf57e75bf7f02a18ae965db26f0d2189d,
a16224226f643245a4c42ddac28d614fbe46d02ea1f8d1dcab91a26eea0c19bb,
bd55995a3f6bffe519366ea7b891e1d006da5472b8de95c5a8c7db52adf2f91a,
c946c76414f1c4b5f5825e4cb5fcda7a5aacde9fa0ce1c478caec1f3d812c606,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-5}\label{bandersnatch_sha-512_ell2_pedersen---vector-5}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
-,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
08fbea5cbe5af93a1529c222d6b3fcc672599e59261d9ed485ef45146befeb03,
cdf7907e1902ab6989732bd5824171912905725296e86d2d864ed0eea5322d54,
02667d1f512990e80b127eed9139ae5590853fde2469e177fee5fa0908de1fc2,
c2d48dada6adf017c2ed658fd91789e4b63f2d6b894ce98fbfef97c56ed4d5d5,
48c13fd4d2cbe731e7ecbf9cef6b2fa5c1a55f27bc0f34753cc211d7cbff7103,
78c5b906fbbca6466120cd079bf7fcdecedc1db7916ed74dbf3ddc2f5063b81a,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-6}\label{bandersnatch_sha-512_ell2_pedersen---vector-6}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
c8b1ce7a665f75506e6a64ef52aa7d8cbfecde0ad83946eb980ba4d06580f819,
635ccf83a424afe87946a36a532f2f2dd4e72b280f9a8d04e4abe3b7f3cbd89c,
3b15fefece933682d3a92dc57fdaa4da6e76f80c41cb926b00376576bced3668,
4b24cd4a4c25aa29aae4e969cf5be562cb9ea176593f8c06bb7343c8da71eac0,
3278c30b9d2fd950fa1a6e82e98375c8fd651f237806f8eaab44c0817b2cad10,
d59f47aa43f471c63ff9cebbab2aaea14feeeb914a3e1a9589350864f3d7b902,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_pedersen -
vector-7}\label{bandersnatch_sha-512_ell2_pedersen---vector-7}

\begin{verbatim}
9504efbeadf81b20a9cb64c1331915eb3718a574227458230d1d80dfa94e8b13,
704fd3784947de4db4fdcf0b477530d094bf5a656707b7d6cb43edbc4db7336b,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
1617b4fca3d7354fd43ae783bd6d0cfc526a80e257fcccfdf8e4d87e74dd7c6d,
6b279b85a1c55f55db80167e6bee997a5bf25c1767ffc2a34ae696baf606f5a0,
3a19e858c8f2cc41037737c43d23dbf3d124ea7059d30c6ab88aa184e14fe20c,
0a9e31ccc09e5464e53afa2057098da6208478f9334199c60bd4bc7443a3d5c5,
1ce7b8f6bcf3723106588842207b1199b8feaaf3bcc13874c0fa2e82a53b47b3,
7372c8e03008802e1bfdf4ac6b8832aded5b48ddb688af168cb67a882628ba22,
4b61c4d7d6179d8e1fe407a20e1ab22acec0a4834eb36fe03f254480d9d87e1b,
40d1a91ac8b287a2b754e9ba05c7c2091e140f0fb40753ebbd2573b6e9d1f514,
\end{verbatim}

\subsection{C.4. Ring VRF Test
Vectors}\label{c.4.-ring-vrf-test-vectors}

KZG SRS parameters are derived from Zcash BLS12-381
\href{https://zfnd.org/conclusion-of-the-powers-of-tau-ceremony}{powers
of tau ceremony}.

The evaluations for the ZK domain items, specifically the evaluations of
the last three items in the evaluation domain \(\mathbb{D}\), are set to
0 rather than being randomly generated.

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
blinding: Blinding factor,
proof_pk_com (Y^-): Pedersen proof public key commitment,
proof_r: Pedersen proof 'R' component,
proof_ok: Pedersen proof 'O_k' component,
proof_s: Pedersen proof 's' component,
proof_sb: Pedersen proof 's_b' component,
ring_pks: Ring public keys,
ring_pks_com: Ring public keys commitment,
ring_proof: Ring proof
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-1}\label{bandersnatch_sha-512_ell2_ring---vector-1}

\begin{verbatim}
c9922b7a9849b9928e15c655dd2f22ceef737cc355024f43d4b04bf4398c270d,
5a538209ff1fc7b1c9c8e1da05b3e169acf10a8b1591b3af029fe4eede0bbc71,
-,
-,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
54421f7ffc399872f1cb868efbb7eef4034178f1e369cebfb964ca61e4f3f256,
7b89f2aba6af7474694f24f75adf48336e00dcc8f3ac889ef4daa53c859497a6,
afa1000852c300cbf235a6955ec4105b01919fa67ec6cc92ec92100f19c25809,
680539c070ebcaca50c4bf201869c2c355f1467e1b8ece6e0bcafc466872c5cf,
375a8ec2e95f58a41ea09090f9560e580e7a3cc67998129fa98dac1da5d0850e,
5071efbef9428b2a26eb09440891c6829bc0c57b4254ca811ce453a0d5938dea,
7dc8aa043b28383d334ef500fd7d770d35ab1c5ebc28df0807215911f4ab2d10,
045343af67f88d35679beab125c38b80029099b746ea47ef3eb488b1d38d130d,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..5a538209ff1fc7b1c9c8e1da05b3e169acf10a8b1591b3af029fe4eede0bbc71
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
b0b98118b398c44a391065d9ff7d1afb3b7d3ce2c4d81db787ccf6f7d90cf36c
..8e15688183f5e4c1d2688aaaf289a4448c2b9665fc06b8d1fbb42010f1c7b7c6
..1669f4a2922bd9ec90ba95f5bc8e4cc6d3faa1af74a2a83f3a5870c15f4e18cf
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
a88f3e5041ce58a9b730391fdf31004a4eceec666a600ccf443b0ba82c478c88
..fea31f106453618afb82ae847d905cad9107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..9544919af606752d54cabaa6a28c30762a42fb27d7347aa3a7d95e6451d735c7
..db7395793dc4ee1e2a63ab02c0d112baa66816f64eafad9351b9e11386a79abd
..3652805e5244bd13cf00e5d949c252d2977610d9721e05d699bc73b14bf2b5d4
..d9491f72803a1165a82f7ec4c02e177dfec115f10c24980fc1148b20d188c839
..da5923eed4679b688d28225fc9fa01d0b4c8c84c96d318cee216c718a35aef04
..7587f52fb5ff09acf3e109feb54b0d0f34fbf8fec8465b37e478edb5a055cc2d
..d4f01d358a5b3c5f6ba74973e363eb3f58e5b9b59342fb5d34516fc360b9500c
..edc3e7e7182e2800d8599daf5f198c8dd21bab8faf01ba6d7567f26c79b3063a
..621181498e89b13e4954db72cb5a7c5179ef74424a6ccd2b34d9919361565236
..cc3a3d0dd91d680f84d19c9f78a4619bdf127c52e636b5b56726af7644f6c553
..a72102f6b8d96baed533806d665d961a6a999fb8b563c2af2b99381067a2ca27
..48c328ab92bf96d34200d14a3032f46f27106ce65d6fbe17cc47d0574e080536
..da27459afccd64dbbe7d45ba41ed4a64a63604043ca130ed5bf0ab1a179cd7d5
..9c52cc8c088864bb16f9bc2256329448044860fd850c337eb162ce909ca80b89
..aa5e660e1563aaa6c1cc007b5070711fa55d4976548e56c9657c973aae29f3fe
..3485705690bb6718a47a6b1b175b879c,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-2}\label{bandersnatch_sha-512_ell2_ring---vector-2}

\begin{verbatim}
0b4259ca1b10c9ed462532639113e1caf26b3a1a2d9e91ecef2fc5c2d23aed0a,
ff341f0c9da793b2d8fef91bcbfd5b55c2185352e4289edc1dd6c64e3fe09b0d,
0a,
-,
8ec04d55a790d47cd32c5062cb44517f164515dac88a8ea6d972db1a7da08abf,
e20e48a14d1ab23cad04e8bc39705d194e87587072fe2e7114d1f85fd7fb6105,
f7f5da876f037509854307d89273b14ef5db4f0971df0879963e1bf0e775636f,
da3304d52c2a64ea75504ac44776e5e4900a38eb9a61f9478285aeccba6ec41c,
a356a2fafe785bc79860ef65534df7c1a2ee7d45ff6db649537dac1687ae4785,
ec546c1932f72e146a0e45d7107c97e99aacc9c72fd6ae6fd0b0417124aa26ca,
1d661c6349b33182ec77b58457f6d45dd9a618017ea021b986cf1eff18c4ef95,
1e8eb9a8cf017c6a50d0f947f9bf02575b60c714c81602a8f06965ec7e67c300,
49c44ad19ea4aaadfc98c2586660dbf3d8a434bb062fa948d82fd4a717ac5f12,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..ff341f0c9da793b2d8fef91bcbfd5b55c2185352e4289edc1dd6c64e3fe09b0d
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
94f0f18ec9f0593fa1bfff259f33600653fbe62a665e9345bcf5149fbf0cf52d
..9748bfc8b7c40c01a11736a7cf55239dac1956d482d4cd466e1f921e52ae5f0f
..ce92c3bc53844977507630d6add31b2674046761607c3131567fac4ca610e985
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
b1db26d63b3147361513641ced7124d32642eb1246aefd0c25495387ec3e8a1d
..fd1ffe4870e37ce5e3a5ac300a507bc39107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..a9af4c62f6d00e23d85b14c83e8d8ec6948a30871c2171ec2c98b78bd3c542d1
..ad95025cf9e2fdfda6d6926e42e6a2478b80aeedf10a587fe26c1feb19481f7a
..043eab9d3bafdda49ee2b32079524f9c5277df8ff2e976341b009ba470fe04a1
..b720d6cc520eb9b6e15d7d590ce8105ebbd9064bb8c6f10aab02ed91dc1c0430
..f70441bb8375bcf61ecb1b93b1ea8661634b7ebcf379fb16f7565e1fcb889971
..c38ae9824ce3afdf4b0253bcafd1da0240c67a07516e4966fba334cbbb7d5b73
..233c8b0fbdbb229398ebbf0d2d5b993733d2e288d02555b0bd1c78c297d0b62f
..ac56252e2080bcbc1a62f3de4c601995b976957fd1e60a69a8eed5d470405358
..79a4c050ac105812d55ed2d4ec454f1d3ad8b59bec359e2d596f222d837cce31
..efd614b86268d1290911c46c6445590ee5eb7b08f7aef20cbc0ee2c210e24503
..900314cd1cec12f509bebf7256c83d810014348189272f076b2ef91384257827
..899f7c5971c37b8f0f2796979770999a8a4c22e7bdbe138dbd37941b09b1649c
..30e5484b3e73a08bdf92d3a928546722a1d9570ff2a7a6688dac5a7687d48021
..649b9ec86d648f1094cb5fad173cc88b5aad0ff3c26606aa6af9d8c46c491bc6
..91bae6269d202b0fc85bcfe806ffff37a0e9fd9d91d3c75e9be7952042c5d087
..90b01bf994ec674b531323d263a62678,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-3}\label{bandersnatch_sha-512_ell2_ring---vector-3}

\begin{verbatim}
dd60163595ff312a49aa5849917ba19020038ccd42f8a1d468da0973079bdb15,
fbba8feb488e767b9864726fffdc8595896757430eba9162a1a5d9a03381d5a4,
-,
0b8c,
f508a4e84812ee3dce73ef72bb9064308128384b4801f81ef8616a7dffc486bc,
719ace6342e2c5b3615e33d6e081c6ffbf0813f3f42ccbdf92973869fab0bbe5,
cc87c37551a222fe1207655f20225cb79a3dc2ebcefd7111550911e36423ad62,
3dd321bf1fbbafd76d48c000a28768152e919789bd57cd50d5e17c88a1baec0a,
6d16e2ff7b28a8880499e34cfe6ffbb1d12efc27675af3fef635e8761c893dee,
5311bd0755a2bbc6db01b930526e85120af5189e2fb259fc941f3acb1611d6eb,
3c4ea965693b470b0da4f9c9508da97dfa70e5e85ee78fbd3af377a2298b4864,
a48a2f80da4190ec19e293a50bbc1bc047ebc38a14f4f19f97f5daec48ab4205,
eb91c85fb3b211f1ec63612950d04c78fc19a760294d01bd82f9218e944b640d,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..fbba8feb488e767b9864726fffdc8595896757430eba9162a1a5d9a03381d5a4
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
92c975ae43de7bd1bbbcb3ebf6f04e99136472c8e665c48618ab06171f96fe69
..3f2f12089ac66e5f79a68b1bff5b7076b1584cd580607934a1d1e0feb12c9bcd
..60440b83a85d8f142a9a3834b3da1c157fc80f1684ab0eb21e70b8b1ae571768
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
b5aad40d12b343366083f9a84c186d2dfbd6ebd7573f1ef7ff14e49c9e1baaf6
..4b62f751e821188ed13b329dfd4e4d799107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..8e0ac886ab6a40f4e54281fc4698174ddfd2621259950c659c102629b7dae6d0
..5e47219066b2725d95df23e8dee5b1d683e8d9403bdafa74979c83014c7eaad0
..3c96a5eb7966e44f2a46f291fcde1b8074f3a781bdebcf0a16da471c90846f5e
..b7a9bef19b200f0adaefe85adee6cab46adce74aff1133c853cce2ce2a96133c
..e996256dae7b294ff36a6ee0841ccc622f9799c6835ef8c3456232963d1bcf68
..d22d33ca2f73826b94bb365582baf7c69eaaa14f7ae54ec6a28f6a232b34cb5d
..861d411d57a1df938f88ed517cb109c4c8daa4d678cf5aacf3bb391932e9ce65
..111fd51782ce82119806a18fe799238ca4753517ddc2fdb3557fc51d809a9b2b
..8d72462b09ca852d5c146de0f8b3feeaf0528606ef096164af793423b7830342
..234fa6a96a895e27f9ffb37ba9246b29ad4c2db52acde665bd22913b56bdb216
..b2fa26e5b91dfa8d6a2ec1c6f002cb4596d65784e4b283b011f2c9bd1b47ea5c
..4b662b6db72fe2f53cea7ae575ac7c7f9008e7e1f70ad6f29b702fd147e44a15
..c1901edad5b587830e2a847a4fe72264b983933c1ac9cdcd09d5bd7cb6e61600
..c191acf69113095c03dbbe17f6c1d50ba8aca3afc64f9f8cebfddbb05347a760
..a1763564cfb18d1313f48f6484f763ca499bc68b43057969a9ca1e27fb0cf781
..a8f48bcfd3b25b83a5738a35039854e2,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-4}\label{bandersnatch_sha-512_ell2_ring---vector-4}

\begin{verbatim}
dfc32f03fe9487f123f2afeeb9487cb6b1eb23efac24a60ae540f5aa632ddd18,
f8487052801a89161424ee745189b5f7fe568819b9f13f44a8b3d173b57e928a,
73616d706c65,
-,
fa6a45172b622ddaccbcf7a3b2d91a36ba504598a83d5a4ed23b416063e4e039,
8f3ee5f3e386775c13093f84678e01594419d747a7037619fa7ea20790044218,
67c6fbdf10f3b5abec5c5ea368662455aa1cac36a6a17621ddb2b526c52fd8dc,
b3f08962012e4f4aa9e6482d7d682275ac98e57f099b991947fad5a53451d51b,
1c48e5ce0ae9b3e7a09626bc1333544f1dbe5033d5efd591a059b04a41830eb6,
17b630103915e544c1b4b1a3e8cbad9cf57e75bf7f02a18ae965db26f0d2189d,
a16224226f643245a4c42ddac28d614fbe46d02ea1f8d1dcab91a26eea0c19bb,
bd55995a3f6bffe519366ea7b891e1d006da5472b8de95c5a8c7db52adf2f91a,
c946c76414f1c4b5f5825e4cb5fcda7a5aacde9fa0ce1c478caec1f3d812c606,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..f8487052801a89161424ee745189b5f7fe568819b9f13f44a8b3d173b57e928a
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
8f3bd322dd602f42115519028e1261ee1dd456a7a8a92363b4ce733d53a80ba8
..d0414bdbd3634ac75487ec03a4f4458d975014f4832268b15b43cf23c2fb09f6
..056f3a8eb1881ed4d7e2d5e1f0e07dbc0bd7686c04c1a9ab906578736efbbf7e
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
98e9ae043bf407a800c73f16585b9fa74acd7c09038d04af53da2583d62c3b2a
..1ad6ccbe263f6f62547067f35c7bae909107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..b41e837b06a596792ebe4847f044a1c9992b00d425cefd37e7ae8cbb99b8fe8d
..25ef49e0dca6b4b354921967a6f9e03c956a9a5558912ecde5539854c9958692
..566557a9f9a81546baf91617fd41e3c7960848e584e2d1d35a8be5ac5911086d
..d7d1f3b32411b9bdf92b9b9ff47fc0ad5c172662e9eaaccf7300f350b740b239
..c9213c270f1ab0f7b7fd115b4fcf30ddbdbe14b21872cdd4cc3f6260f92e2621
..555fa06619f164d0116d58670925e74e5579140c388b463a39cceef4734ae321
..b7b9c79ec2d4b778c457aff910e27296956483eb1c00fb5df65b6032a7962d71
..8ce87bc2ecfdb519f71a2ef2cf37ce234c065fd820e7d46aa9b4910fca9fcb0f
..e887bd3d99ebdbdaee2dd94c00e1ba286d71da97d804f2eb9e90045974548f18
..59546e0e5603ec3acb11f20cf3aa513ebb45af6e501329654076b8be4eba5f08
..aac72327767b0be36cddd535a4aa866d317cc441c3cae05ab36510aa0080ea4e
..24e1e2e837880ca0cae490f7e9866e92a5ae3904b7cf79a8de01fdc3b2d29284
..0b4b8bb0a50c6d3f84e59c18131db932872ac971a15e0a883e0de6ca79795e0f
..a04adb0d3ce7e2b7517ee8b12a6348f267439319cd1fec9d5977a7d9091b0f34
..aafeae086a35677fb741acb5437d8bd9d64e2649ad0aa62244b90d106d068fc7
..e0859d7bed816a3bef6dcb33dc009459,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-5}\label{bandersnatch_sha-512_ell2_ring---vector-5}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
-,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
08fbea5cbe5af93a1529c222d6b3fcc672599e59261d9ed485ef45146befeb03,
cdf7907e1902ab6989732bd5824171912905725296e86d2d864ed0eea5322d54,
02667d1f512990e80b127eed9139ae5590853fde2469e177fee5fa0908de1fc2,
c2d48dada6adf017c2ed658fd91789e4b63f2d6b894ce98fbfef97c56ed4d5d5,
48c13fd4d2cbe731e7ecbf9cef6b2fa5c1a55f27bc0f34753cc211d7cbff7103,
78c5b906fbbca6466120cd079bf7fcdecedc1db7916ed74dbf3ddc2f5063b81a,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
b4f43f81bf0b79c4b144d8ba8f7975bb12b512aa15ddc53e5eef73647b6fbcde
..47697176d801d29de4270293a68d328891798ba7a2d045a4c403f647619ab997
..54f593d73de9b09e1d65d29cc60a083b9677f9b2c8f6d66142908e6778d29a3d
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
87b659658d78c2d7154006f0592e159386828c8ee3955ad4795ed2751cd061d1
..238b1bb57c402937481854ab9a0e52a09107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..8d75886422670dd4bf46279c1914efae398dc1cd5724b1bfc8780470ed67db63
..932f28ea195e4d836ee4cd58d054ab88a2d5bf2660bb37b0756c9fc8a8bd5d81
..699b208bb25689c9d90142c774f4310404ef03af8a41301c5a7be003edf060f9
..66037ce81d3526a84e86a417df80bb6910f77b801ee82bf2f1a7d593d024ec1b
..e4feacca619ab375e247a6cab09c64dd221d567e649c5735c738d10450388a2e
..72e8d49a4006cb45b0e32439f61d6578cd6700abb863da52a2f078526aa42669
..b524d4626b936ed0e957c711cddc03584a22a2b0fde46f7c3b7a60160c72ef35
..4b1dccbb231d4a2b6a26f28713fa7ffab4deb1141529dede42fd066fc929755a
..7e1c1ef71ed98a5d44ab20176f8c120215444058ac0b8521472a664a33c0d843
..1edfe789f6221ccc33644748d9347bd900f8e1ea008b7cf83ed931bdfd4d9d63
..aab1165d23aa23bfc0f49aba962080de70ff5c3457343858799d7b7a12c48945
..cada1ba8c461586e367f125fee0ec7b0c02efd913b89b80e633bd59a3c6a1d08
..ef98f1aea1f5528b07408981b15a606cb14596953ba42f5b18d681922c3bc3f0
..773d1cf7566d543202c3db456f1f95fd460081ff6759da8c0caf6f90a431df7f
..9171d5ad8046ec651e76c019ae1c5f94e00cc3889dcdc1115cc53fd0fd548c79
..af1ef586376f6447f1224d879a1d393c,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-6}\label{bandersnatch_sha-512_ell2_ring---vector-6}

\begin{verbatim}
04d3da92994eb327893f747b5aee14f82353ca88f909585b492ac6124c52da07,
6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
a99080c7bb9f8f4ccf68aa2cc8a946b03dbf07735564a5102009f2c8e5013bd2,
d52ea29fddc6c87f38e5d56ef2f5af434f90f28e8e122dd99284076b57d29997,
c8b1ce7a665f75506e6a64ef52aa7d8cbfecde0ad83946eb980ba4d06580f819,
635ccf83a424afe87946a36a532f2f2dd4e72b280f9a8d04e4abe3b7f3cbd89c,
3b15fefece933682d3a92dc57fdaa4da6e76f80c41cb926b00376576bced3668,
4b24cd4a4c25aa29aae4e969cf5be562cb9ea176593f8c06bb7343c8da71eac0,
3278c30b9d2fd950fa1a6e82e98375c8fd651f237806f8eaab44c0817b2cad10,
d59f47aa43f471c63ff9cebbab2aaea14feeeb914a3e1a9589350864f3d7b902,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..6be56f1a0c32af7ff857e278dc9a0dfeaf724b5961ab0a0147663f77d3e0dfb4
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
b4f43f81bf0b79c4b144d8ba8f7975bb12b512aa15ddc53e5eef73647b6fbcde
..47697176d801d29de4270293a68d328891798ba7a2d045a4c403f647619ab997
..54f593d73de9b09e1d65d29cc60a083b9677f9b2c8f6d66142908e6778d29a3d
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
875e6616f4d39dcb1bd8dbac51fd6fbf54e2fc24ee641cadd283138cff4dd31b
..a336f7ecc1d29923a6330679a822cc4c9107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..84e134c22a168085546b5d1e770cb1c578a253a6344209aa346a242ff62459fd
..ab5a3024f74ba6842ab2aedbdd25f47d951f863a44c3712e65ee38496cbcacf1
..73560adec3b143ceac2e42cd0ed1beebecbc59ee1bfea5346144b2f9ecc9acd2
..c7be098013600886cf8f8dfecf5775918c843a72ff0d5123161b0baf7f827d53
..00e134fa0e9c02810d598a665c28a69b470c0bb3049f29e2e21604d403d05365
..803065bd1b8887d6f7d73a8bce144fe03c8573978b3891ca67dd254f61e4b444
..b2e54e83e53a0beefb24ec34eba6886fa21ffe3de8eca9a5f8a739f56f5a873d
..85b99984380564f9992b105c5dd9f5df1d5586748abfe52be134071de4ffef23
..368afdc6fdbe75587780b667108599aa4ea4051fcacd83fdc52f31a26fe60d71
..f614c50746be5d68abf785d2e13656744c1463a32f55f6604568d50f9b4af52c
..8ffc4cbdb78b88ccdcc826d32f1b1bb2f44b3fde506dd6379a5bd6dc642202e0
..b220ebcbf7a60fe6045489717bb2b7cef209be9642142e3f88a54d70d12e228e
..9d70c0e400ed72b39b8fa0805bd4a76a8aba88ca324dedb1aa1778ce58527900
..35885e4a2982da28a28044c50e7f2b2e18e473ed76e13c0778bb88128b206bba
..b59b7a2fb6ac7c8b852ec8af45c84bb95f8fa3736d57addea168c2381668067c
..ae4e3cb4c72bb3b2b724e582c62faf45,
\end{verbatim}

\subsubsection{bandersnatch\_sha-512\_ell2\_ring -
vector-7}\label{bandersnatch_sha-512_ell2_ring---vector-7}

\begin{verbatim}
9504efbeadf81b20a9cb64c1331915eb3718a574227458230d1d80dfa94e8b13,
704fd3784947de4db4fdcf0b477530d094bf5a656707b7d6cb43edbc4db7336b,
42616e646572736e6174636820766563746f72,
1f42,
832414b806b4dd6f98117818f1518667c8bb2bd625dfe353b1f2d22d4f32ead6,
1617b4fca3d7354fd43ae783bd6d0cfc526a80e257fcccfdf8e4d87e74dd7c6d,
6b279b85a1c55f55db80167e6bee997a5bf25c1767ffc2a34ae696baf606f5a0,
3a19e858c8f2cc41037737c43d23dbf3d124ea7059d30c6ab88aa184e14fe20c,
0a9e31ccc09e5464e53afa2057098da6208478f9334199c60bd4bc7443a3d5c5,
1ce7b8f6bcf3723106588842207b1199b8feaaf3bcc13874c0fa2e82a53b47b3,
7372c8e03008802e1bfdf4ac6b8832aded5b48ddb688af168cb67a882628ba22,
4b61c4d7d6179d8e1fe407a20e1ab22acec0a4834eb36fe03f254480d9d87e1b,
40d1a91ac8b287a2b754e9ba05c7c2091e140f0fb40753ebbd2573b6e9d1f514,
8b3031022897595ba3a280d6af047a46498f6fbfd62081d1df6a2e4b713014df
..bd7fcb7c0956648c043bc345a8fb3e1a2c73815bf87f6c3cb985a00c9e95e991
..307d3bef5e82f857b97f987da190e5fc6d77a9d24ac2068b701df1ab0487a1d8
..704fd3784947de4db4fdcf0b477530d094bf5a656707b7d6cb43edbc4db7336b
..72ce1e7899c633b92709702bdfbe74347d9bdcd1ad62b13f960ade3d1df899b3
..73154c7a701d5d6d38216c4be09800c024c35e4739e43f2b7aa5e0b55a281757
..a4cc78b2e3eb6a19a777ff20bb801c043f73d836aab81038e286560e260922b4
..0c5335e7855f8a38e9ffada8eadb2415f82b5822319fa53b66ef1c0469048ec3,
b3982b5838293b8fb58f52511cda9ebcab48a5f0932edf817630dccc230eb651
..a8f97ce4fd078b7af816329f5739ee12a2fb2031f85fac1ef27137ad68e5ae0a
..befb844f516a67641847b265eb1a353652fce946342f487d95b0a538e229d6e0
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
8048dbacf65522f4ad29d64c1eaa2e914a308bd0a69de81499436e9b516fd8cc
..ec4512abea7dcf27175f52b9be39f03e9107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..84989a9448a7393c6bf91ee89971748708c643a365b42421005e76c9eefaf024
..5b0d762f85a9fccd4900ed88d4a4ff85b7272746c0f19acc2c729f4b6ac50df5
..f6f3dc464fd39b4c4b8311b87600d9073bcba43577b41970105c75634edd2717
..d74a8975ace0661a7b1bd57765b5a430f6b38eed1f8eaa6e2440537e99f48a2c
..9237209d43328fd9ae447a610e0e4becca103208ee7b4e0bd6acf9ac267b0f13
..2700412904e580ec794b7af75f7d30224502b4facb29ff44ebb4d2fd80db9902
..edbdd1dc1e65466a356f46b1d2132103f86039f13114f3e06c98bab560d2e71d
..2f2dbd01e6b32a220f7ecefd812aed740bc1ef95bbd5b7d49a41ad56de8f3635
..2f2edf247ee7169a5927232c66a889aa11084a36b890582d9951168628cde057
..ab0290cd106583fe09a6c40c581e4b1f269eac69ac5e277911d0d3a41a701b2a
..a8cea5c7bc96efd03bd968045c1aee5e9cfd55c191256aae97445370e7d52ec5
..910a208a47b8cd30ac784acbc0e46cc33321cd7e3ba824206e7ee4de69bcb718
..b02b7514a55b89765a3743de28818b1f95901c7f1465e1287c83fe0f98320047
..4eda63eab68a605438860fe1d8ce88992a04b7bf621fd3c63a462917404d9091
..81c6a5a15e7c8ef381a59b22c3acfd5c66320a413ea393f08bd755e2a9463c3d
..a85ab2ff7e6311f41dc80fe6d0c798c1,
\end{verbatim}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-RFC9381}
1. Internet Engineering Task Force \emph{{Verifiable Random Functions}};
{RFC Editor}, 2023; \url{https://datatracker.ietf.org/doc/rfc9381}.

\bibitem[\citeproctext]{ref-BCHSV23}
2. Burdges, J.; Ciobotaru, O.; Alper, H.K.; Stewart, A.; Vasilyev, S.
Ring Verifiable Random Functions and Zero-Knowledge Continuations 2023;
\url{https://eprint.iacr.org/2023/002}.

\bibitem[\citeproctext]{ref-CSSV22}
3. Ciobotaru, O.; Shirazi, F.; Stewart, A.; Vasilyev, S. Accountable
Light Client Systems for PoS Blockchains 2022;
\url{https://eprint.iacr.org/2022/1205}.

\bibitem[\citeproctext]{ref-MSZ21}
4. Masson, S.; Sanso, A.; Zhang, Z. Bandersnatch: A Fast Elliptic Curve
Built over the BLS12-381 Scalar Field 2021;
\url{https://eprint.iacr.org/2021/1152}.

\bibitem[\citeproctext]{ref-VG24}
5. Vasilyev, S.; Galassi, D. Ring Proof Technical Specification 2024;
\url{https://github.com/davxy/ring-proof-spec}.

\bibitem[\citeproctext]{ref-RFC9380}
6. Internet Engineering Task Force \emph{{Hashing to Elliptic Curves}};
{RFC Editor}, 2023; \url{https://datatracker.ietf.org/doc/rfc9380}.

\end{CSLReferences}

\end{document}
